\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
  \item\small{
  	\ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
  }
}

\usepackage[dvipsnames]{xcolor}
\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
      {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Saveliy Romanov}} \\ Email: \href{mailto:romanovsavelij@mail.ru}{romanovsavelij@mail.ru} \\
  LinkedIn: \href{www.linkedin.com/in/romanovsavelij}{www.linkedin.com/in/romanovsavelij} \\
  Github: \href{https://github.com/romanovsavelij}{github.com/romanovsavelij}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Yandex School of Data Analysis}{Moscow, Russia}
      {Master’s level program in Computer Science and Data Analysis}{2021 -- 2023 (Present)}
    \resumeSubheading
      {Moscow Institute of Physics and Technology}{Moscow, Russia}
      {Bachelor in Applied Math and Computer Science}{2019 -- 2023 (Present)}
    \resumeSubheading
      {University of California Irvine}{Irvine, CA}
      {Coursera course on Go language, \href{https://www.coursera.org/account/accomplishments/specialization/certificate/2QEP6H7M4BRC}{certified}}{2021 Jun -- 2021 Jul}
    \resumeSubheading
      {Samsung IT School}{Moscow, Russia}
      {Completed Android development course with a gold medal.}{2019 Sep -- 2019 Jul}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
      \resumeExpSubheading
      {Ozon, Search}{Moscow, Russia}
      {Software Engineer}{Jul 2021 -- Present}
      {\skill{Go} \skill{PostgreSQL} \skill{Kafka} \skill{Redis} \skill{Memcached} \skill{gRPC}}
      \resumeDesc{
      Ozon is the most popular e-commerce in Russia with 100 million MAU.
      \begin{itemize}
          \item Created service from scratch for handling product categories, which powered new classified business unit. Classified project is estimated to have GMV \footnote{GMV ~--- gross merchandise volume} 15 billions USD anually.
          \item Enabled search flow localization, which caused company GMV growth by 20 millions USD anually.
          \item Implemented dynamic products delivery speed filter.
      \end{itemize}}
      
      \resumeExpSubheading
      {Moscow Institute of Physics and Technology}{Moscow, Russia}
      {Teaching assistant}{Sep 2021 -- May 2022}
      {\skill{Linux} \skill{C} \skill{Assembly}}
      Teaching second-year students at the best Russian Computer Science program.
      \resumeDesc{
      \begin{itemize}
          \item \textbf{Teaching assistant - The Architecture of Computers and Operating Systems}: discuss lecture material with students on 1:1 meeting sessions, review code.
      \end{itemize}}
      
      \resumeExpSubheading
      {Biletarium}{Moscow, Russia}
      {Software Engineer (Contract)}{Jan 2021 -- Jul 2021}
      {\skill{Python} \skill{FastAPI} \skill{MongoDB}}
      \resumeDesc{
      Founding backend developer of a \href{https://biletarium.com/}{website} for buying museum tickets, that was developed for the Federal Agency for Tourism.
      }
      
      \resumeExpSubheading
      {GlowByte consulting}{Moscow, Russia}
      {Software Engineer (Internship)}{Jul 2020 -- Oct 2020}
      {\skill{Python} \skill{Django} \skill{Numpy} \skill{BeatifulSoup}}
      \resumeDesc{
      Developed from scratch a service for searching for a promising location to open a new retail store.
      }
      
      \resumeExpSubheading
      {Cordet (MedTech startup)}{Mountain View, CA (Remote)}
      {Software Engineer (Contract)}{Apr 2020 -- Jul 2020}
      {\skill{Go} \skill{PostgreSQL} \skill{Docker} \skill{Redis} \skill{Prometheus}}
      \resumeDesc{
      \begin{itemize}
          \item Developed registration module and a microservice for user forms processing.
          \item Set up the monitoring infrastructure. 
      \end{itemize}}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{TikTok comments fetcher}
      {\href{https://github.com/romanovsavelij/TikTokCommentsFetcher}{Open source script} for parsing TikTok comments from the web version.}
    \resumeSubItem{MathDailyBot}
      {\href{https://github.com/romanovsavelij/MathDailyBot}{Telegram bot} that sends you math problems daily and verifies your answers.}
    \resumeSubItem{JIT C compiler}
      {C expressions compiler for ARM that is written in C. It translates C code into syntax tree, than into assembly instructions and finally into machine codes.}
    \resumeSubItem{Formal automata minimization}
    {Deterministic finite automaton minimization. It was a \href{https://github.com/romanovsavelij/FormalAutomataMinimization}{task} from Formals MIPT course.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Go, Python, C++, C, Rust, Java, Typescript }
   }
   \item {
     \textbf{Technologies}{: PostgreSQL, Kafka, Docker, Redis, Memcached, gRPC, Kubernetes, MongoDB, Django, SQL, Prometheus, Grafana, CI/CD, Selenium}
   }
   \item{
     \textbf{Knowledge}{: Algorithms, Data Structures, Concurrent Computing, Distributed Systems, Databases}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
